Pool Model - A unified Mathematical\\ Modeling Framework for Food Science

### 2025-11-28 paper/pool_model.tex
adapt figure description to new parameters

        All curves were calculated using the model (\ref{eq:ode_3pool_resource2}) with parameters $\alpha=2.5~\mathrm{s}^{-1}$, $\mu'=0.5~\mathrm{s}^{-1}$, $N_t = 10^4$.
        The blue curve shows a significant dip in the behavior of the system where the death of the bacteria is present $\mu = 0.5~\mathrm{s}^{-1}$.

>>>>

        All curves were calculated using the model (\ref{eq:ode_3pool_resource2}) with parameters $\alpha=2.5~\mathrm{s}^{-1}$, $\mu'=0.1~\mathrm{s}^{-1}$, $N_t = 10^4$.
        The blue curve includes cell-death of the bacteria in the lag phase $\mu = 0.15~\mathrm{s}^{-1}$ and thus exhibits a small dip before its exponential growth.
